\documentclass[11pt,a4paper]{article}

% Packages
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{geometry}
\usepackage{amsmath,amssymb}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{enumitem}

% Page geometry - optimized for professional appearance
\geometry{
    a4paper,
    left=2.5cm,
    right=2.5cm,
    top=2.5cm,
    bottom=2.5cm,
    headheight=14pt
}

% Code listing style
\lstset{
    basicstyle=\ttfamily\small,
    keywordstyle=\color{blue},
    commentstyle=\color{gray},
    stringstyle=\color{red},
    showstringspaces=false,
    breaklines=true,
    frame=single,
    numbers=left,
    numberstyle=\tiny\color{gray}
}

% Hyperref setup
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    citecolor=blue,
    urlcolor=blue
}

% Title information
\title{\textbf{NutriScore ML Predictor using OpenFoodFacts Data}}

\author{
    Jacopo Parretti, Cesare Fraccaroli \\
    Student IDs: VR536104, VR533061 \\
    MsC in Artificial Intelligence - Machine Learning course\\
    Academic Year 2025-26
}

\date{}

\begin{document}

\maketitle

\begin{abstract}

    Abstract. 

\end{abstract}


\tableofcontents

\newpage

\section{Motivation and Rationale}

\subsection{Contextual Framework}

To mitigate the rise of NCDs (Non-Communicable Diseases) linked with today's diet standards, having access to nutritional information is essential.
Front-of-Pack labelling tries to help by simplifying the hard task of interpreting nutritional tables. The Nutri-Score serves as a tool for a better, healthier choice by offering an immediate visual cue. The accurate prediction of such grades is important to help people navigate a complex food landscape that today is dominated by ultra-processed foods.
This increased availability has dramatically changed the way the world eats and drinks, with severe negative effects on our health \cite{ncdalliance}.

\subsection{Problem Statement}

The task we are trying to solve is the prediction of the Nutri-Score grade given some data about food and culinary products. The dataset we are using is obtained from the Open Food Facts (\url{https://it.openfoodfacts.org/}) website. The food dataset (\url{https://static.openfoodfacts.org/data/en.openfoodfacts.org.products.csv.gz}) is a vast crowd-sourced dataset. It is large but prone to many errors, invalid and missing data, and different languages.

The Nutri-Score is usually calculated using a deterministic formula that uses fiber, fruits, protein, etc.
However, all this data is not always present in the dataset.
When not all of these nutrients are present, we are left with unclassified products.

\subsection{Rationale}

We want to use Machine Learning in order to solve the problem of unclassified products. Machine learning can act as an approximator capable of predicting the grade based on partial macronutrient data or pattern handling missing or wrong values.
We want to try filling the gap in the dataset by automating the classification.

\subsection{Significance}

We, as MSc students, want to try investigating classification performance in a highly noisy, real-world dataset.
The classification can maybe help the usage of the Open Food Facts dataset for third-party applications or for research.

\section{State of the Art (SOTA)}

The scientific literature regarding the analysis of crowdsourced nutritional databases identifies two big issues: data sparsity and the non-linear nature of quality indices (i.e., Nutri-Score).
While traditional approaches have frequently relied on linear models, these methods fail to preserve macronutrient correlations or capture the discrete thresholds inherent to the calculation algorithm. Simpler Logistic Regression exhibits limitations due to its inability to model the step-wise decision rules typical of the Nutri-Score system.
To address these limitations, the current state of the art consists in multivariate imputation via KNN to preserve the local data structure, combined with non-linear Ensemble models, which are recognized for their robustness in handling outliers and modeling complex relationships within imbalanced datasets \cite{ensemble}.

In this project, we will explore the Random Forest and the XGBoost models as the state-of-the-art ensemble models.
A better solution as provided by this study could be implementing ``missing data imputation techniques based on methods for substituting missing values with statistical prediction: Non-Negative Matrix Factorization (NMF), Multiple Imputations by Chained Equations (MICE), Nonparametric Missing Value Imputation using Random Forest (MissForest), and K-Nearest Neighbors (KNN), and compared them with commonly used approaches - fill-in with mean, fill-in with median'' \cite{imputation}.

\section{Objectives}

The main objective of the project is to develop a robust machine learning framework capable of predicting the Nutri-Score grade (classes A through E) for products in the Open Food Facts database. The main problem is the issue of incomplete nutritional metadata, which in most cases, as we will see, prevents the deterministic calculation of the score for a significant portion of the samples.
To achieve this, the project tries:
\begin{itemize}
    \item \textbf{Algorithmic Benchmarking:} Conduct a comparative analysis between linear models (Logistic Regression), distance-based algorithms (KNN), non-linear methods (SVM with RBF kernel), and ensemble tree methods (Random Forest, XGBoost). The goal is to identify the best model for the approximation of the Nutri-Score.
    \item \textbf{Optimization for Class Imbalance:} To maximize the F1-Macro score rather than simple Accuracy as the primary success criterion. This ensures the model performs reliably across all nutritional grades.
    \item \textbf{Efficiency Analysis:} To evaluate the trade-off between predictive performance and computational cost (training time), identifying a model that is both accurate and scalable.
\end{itemize}

\section{Methodology}

The project uses and elaborates data from the Open Food Facts dataset. The dataset is open source and under the Open Database License. We use the dataset URL to download with a simple Python script.

\subsection{Loading and Filtering}

The total number of rows is over 4 million. Since the size is very large (over 9 GB), we decided to adopt a chunk-based solution: we first split into chunks and then open each chunk to filter the data.
First, we delete the entries that do not have the target variable Nutri-Score grade. After this operation, we have around 1 million products. We decided to keep this set of columns:
\begin{verbatim}
'nutriscore_grade', 'code', 'product_name', 'brands', 'categories', 'countries', 
'energy_100g', 'energy-kcal_100g', 'fat_100g', 'saturated-fat_100g', 
'carbohydrates_100g', 'sugars_100g', 'fiber_100g', 'proteins_100g', 
'salt_100g', 'sodium_100g', 'fruits-vegetables-nuts_100g', 
'fruits-vegetables-nuts-estimate_100g', 'additives_n', 'ingredients_n', 
'nutrition_grade_fr', 'pnns_groups_1', 'pnns_groups_2', 'main_category'
\end{verbatim}
After filtering, we proceed with a sampling of 250,000 products with a set random state to ensure reproducibility.
After this, we performed an exploratory data analysis to check the data.

\subsection{Exploratory Data Analysis}

To better understand the dataset, an exploratory data analysis on the 250k samples is needed.
The project focuses on the prediction of the target variable Nutri-Score grade. Nutri-Score Grade does not appear evenly across all possible values A, B, C, D, E. The random sampling we conducted should guarantee that this can represent well the distribution in all of the dataset.

% GRAFICO TARGET VARIABLE

\textbf{Class imbalance:}
\begin{itemize}
    \item \textbf{A = 14.4\%}
    \item \textbf{B = 11.6\%} (least common)
    \item \textbf{C = 20.5\%}
    \item \textbf{D = 25.2\%}
    \item \textbf{E = 28.2\%} (most common)
\end{itemize}

Then we analyze the missing percentages in the features we selected.
It appears that \texttt{fruits-vegetables-nuts} and \texttt{fruits-vegetables-nuts-estimate} have more than \textbf{95 percent} of missing values.

We now try plotting the skewness of the other features. There are some features that have a high skew value. A skew value of over 300 means that there are some extreme outliers, maybe some invalid or out-of-range data that should be removed.

\begin{verbatim}
energy_100g                                  134000.00
energy-kcal_100g                              32100.00
fat_100g                                      90937.00
saturated-fat_100g                           992276.00
carbohydrates_100g                          8761109.00
sugars_100g                            765433221122.00
fiber_100g                                   938364.00
proteins_100g                               8578293.00
salt_100g                                      3625.00
sodium_100g                                    1450.00
fruits-vegetables-nuts_100g                     100.00
fruits-vegetables-nuts-estimate_100g            100.00
additives_n                                      36.00
\end{verbatim}

After a check on the values, we can clearly see some inconsistencies in the data.

\textbf{Positive skewness} is a structural characteristic of nutritional data. The distribution typically shows high near zero values (\textbf{zero-inflation}) and an elongated right tail.

In the nutritional domain, this pattern is common: the vast majority of products have minimal amounts of specific nutrients (e.g., \texttt{salt} or \texttt{fiber}), while only a small part of specific categories (e.g., \textbf{concentrated sauces} or \textbf{whole-grain cereals}) possess high concentrations.

Now we plot each feature singularly against the target variable to get some insights. Some features like fat, energy, sugars, and saturated fat clearly impact negatively on the Nutri-Score. The ones that seem to have a positive correlation with the Nutri-Score are fruit, vegetables, and nuts; however, as we stated before, they have over 95\% of missing values.

We can now plot the features against each other to see if they have a correlation. To better visualize this, we plot the correlation matrix.
Salt and Sodium have perfect correlation, and so do energy\_100g and energy-kcal\_100g (logically it's just a difference in unit measure). Some other features have some degree of correlation like fat\_100g and saturated\_fat\_100g (one is a subset of the other).

We now proceed to check categorical features. The categorical features we take into exam are Brands, Product Name, Countries, pnns\_group\_1, pnns\_group\_2, categories, and main\_category.
Of these features, most of them have very high cardinality with a lot of unique values. For our models, we can mainly focus on the ones with acceptable cardinality.
\begin{itemize}
    \item \texttt{pnns\_groups\_1} (10 unique)
    \item \texttt{pnns\_groups\_2} (40 unique)
    \item \texttt{countries} (3000 unique)
\end{itemize}

The countries feature has high cardinality and contains acronyms, country names in multiple languages, and inconsistent syntactical formats. Furthermore, many entries consist of multi-label strings where products are associated with several countries simultaneously. To address this, we will subsequently implement a targeted approach to standardize these strings and achieve an effective encoding.

Now that we have gained some insights, we can proceed to the preprocessing stage.

\subsection{Preprocessing}

The preprocessing is done through a scikit-learn transformation pipeline \cite{geron2022hands}. The pipeline is composed of the following steps:
\begin{enumerate}
    \item Missing Value Handling
    \item Outlier Detection and Removal
    \item Categorical Feature Encoding
    \item Feature Engineering
    \item Feature Scaling
    \item Dimensionality Reduction (PCA)
    \item Data Splitting
\end{enumerate}
\subsubsection{Missing Value Handling}
First we drop the features with more than 95\% of missing values. In our case, we dropped the 
features \texttt{fruits-vegetables-nuts-estimate\_100g} and \texttt{fruits-vegetables-nuts\_100g}. Remembre that these features are important for the calculation of the Nutri-
Score with the deterministic formula, so their absence is the exact challenge we are trying to solve with this project. The missing value handling is done through a median imputation. The median imputation is done for the numerical features. For the categorical features, 
the missing values are labeled as 'unknown'.

\subsubsection{Outlier Detection and Removal}
The outlier detection and removal is done through a domain-based and an optional statistical outlier detection. The domain-based outlier detection 
is done for the numerical features, invalid values such as negative values or values outside the valid range(200g in the column \texttt{saturated-fat\_100g}).
The project also implements a statistical outlier removal method. However this method did not produce good results because the domain of nutritional values is made of highly skewed 
values with a lot of outliers that should not be removed. For example olive oil is made almost entirely of fats while other foods don’t 
have fat at all, this is not a valid reason to remove olive oil from the dataset. If the statistical outlier is implemented it removes around 25\% of data from the samples
and models give worse performances overall.

\subsubsection{Categorical Feature Encoding}
The categorical feature encoding operates on the features \texttt{countries}, \texttt{pnns\_groups\_1}, and \texttt{pnns\_groups\_2}.
The \texttt{pnns\_groups\_1} feature is encoded using a one-hot encoding, while The \texttt{pnns\_groups\_2} feature is encoded using a target encoding.
The target encoding is used because it is a high cardinality feature with a lot of unique values.
Target encoding replaces each categorical label with the mean of the target variable for that specific category, 
effectively converting discrete strings into numerical values based on their statistical relationship with the output.
The \texttt{countries} feature presents a more complex case. The feature is a multi-label feature, and it has a lot of 
acronyms and country names in multiple languages. To address this, we implement a mapping of the country names to a canonical form.
This is done by using a generated mapping and the PyCountry library \cite{pycountry2023}. After this, we apply a multi-label binarization and we choose the top 15 
countries by frequency (the top 15 represent 98\% of the data) and the other is set to 'unknown'.

\subsubsection{Feature Engineering}
The feature engineering is done through a transformer that creates the following types of features:
\begin{itemize}
    \item \textbf{Nutritional Ratios:} 4 features:
    \begin{itemize}
        \item \texttt{fat\_to\_protein\_ratio}
        \item \texttt{sugar\_to\_carb\_ratio}
        \item \texttt{saturated\_to\_total\_fat\_ratio}
        \item \texttt{energy\_density}
    \end{itemize}
    \item \textbf{Energy Decomposition:} 4 features:
    \begin{itemize}
        \item \texttt{calories\_from\_fat}
        \item \texttt{calories\_from\_carbs}
        \item \texttt{calories\_from\_protein}
        \item \texttt{energy\_density}
    \end{itemize}
    \item \textbf{Health Threshold Flags:} 3 features:
    \begin{itemize}
        \item \texttt{high\_sugar}
        \item \texttt{high\_salt}
        \item \texttt{high\_fat}
    \end{itemize}
\end{itemize}

\subsubsection{Feature Scaling}
The feature scaling implements three different scalers: StandardScaler, MinMaxScaler, and RobustScaler.
Some features that are highly skewed are transformed with a log1p transformation before the scaling.
%log1p transformation formula
The $\log1p$ transformation is applied to highly skewed features before scaling, which helps reduce the impact of extreme outliers and normalizes the distribution. 
The mathematical formula for the $\log1p$ transformation is:

\begin{equation}
    x' = \log(1 + x)
\end{equation}

where $x$ is the original feature value and $x'$ is the transformed value. This transformation is numerically stable for small $x$ and prevents issues with zeros
 in the data while solving the problem of very big data (example the engineered feature \texttt{fat\_to\_protein\_ratio} if the product has a small value 
 of protein like 0.01 it will explode). 

 Through numerous testing of the models, we found that the StandardScaler is the best scaler for the dataset.
This is probabilly because of the nutritional data distributions. Outliers are important so RobustScaler is not the best choice and MinMaxScaler 
is not the best choice with high skewness.

\subsubsection{Dimensionality Reduction}
The dimensionality reduction is done through Principal Component Analysis (PCA). The wrapper class first filters all numerical features and sets aside the metadata features 
(\texttt{product name}, \texttt{brands}, \texttt{code}).
The variance threshold is set to 0.95. This means that the PCA will retain the features that explain 95\% of the variance in the data.
This is done to reduce the dimensionality of the data and to reduce the number of features.
The reduction is around 25\% of the features (lower variance threshold have been proven to be not good for the model performance).

\subsubsection{Data Splitting}
The data splitting is done through a train, validation, and test split. The split is stratified by the target variable
 to ensure its distribution is the same in all sets \cite{geron2022hands}. 
is the same in all sets. The split is done using a 70/15/15 ratio.
The splits are necessary to evaluate the model performance and to tune the hyperparameters.
To prevent data leakage and avoid data snooping bias, we strictly isolate the training set for model development and parameter estimation,
 ensuring that both the test sets remain completely unseen during the entire development and tuning process.

\subsection{Models}
In this project we explored the following models:
\begin{itemize}
    \item \textbf{Logistic Regression}
    \item \textbf{K-Nearest Neighbors}
    \item \textbf{Support Vector Machine}
    \item \textbf{Random Forest}
    \item \textbf{XGBoost}
\end{itemize}
All of these models are implemented through a wrapper class that implements the BaseModel abstract class.
The wrapper class is responsible for the training, prediction, and evaluation of the models.
This approach allows for easy addition of new models and greatly helped us during the development of the project.
\subsubsection{Logistic Regression}
The logistic regression is the linear model we use as a baseline. It is a simple model that is easy to understand and to interpret and helped us
with the initial testing of the project structure and the preprocessing pipeline.
Logistic Regression computes the probability of a product of being in a certain Nutri-Score grade using a linear combination of the features.
It is quite simple and does not perform very well in the presence of non-linear relationships.

\subsubsection{K-Nearest Neighbors}
The K-Nearest Neighbors is a non-parametric model based on the distance. We decided to use the K-Nearest Neighbors
to try a distance-based model with our dataset.
KNN showed a big gap between the train and the validation accuracy, indicating an overfitting.

\subsubsection{Support Vector Machine}
The Support Vector Machine is a kernel-based model that is used to find the best hyperplane to separate the data.
Since we wanted to explore a non-linear model, we decided to use the Support Vector Machine with a RBF kernel.
SVM is a very powerful model that is able to find the best hyperplane to separate the data. Its training time is
quite long, but the results are quite good.








\section{Experiments \& Results}

\subsection{Experimental Setup}

We trained all five models on the preprocessed dataset of 250,000 samples with a 70/15/15 train/validation/test split. We used stratified splitting to keep the class distribution consistent across sets, which matters because of the imbalance in our data (class E: 28.2\% vs. class B: 11.6\%).

We noticed that accuracy wasn't enough to evaluate performance. Because of the imbalance, a model could get decent accuracy just by doing good on the majority classes (D and E) while failing on minority classes. We chose F1-Macro as our main metric because it weights all classes equally.

We started with default hyperparameters and then tuned based on validation results.
% [INSERT FIGURE: Bar chart comparing F1-Macro scores and training times for all models]

\subsection{Performance Metrics}

Table \ref{tab:results} shows the results for each model on the validation set.

\begin{table}[h]
\centering
\begin{tabular}{lcccccc}
\toprule
\textbf{Model} & \textbf{Accuracy} & \textbf{F1-Macro} & \textbf{Precision} & \textbf{Recall} & \textbf{Time (s)} \\
\midrule
Logistic Regression & 0.702 & 0.681 & 0.679 & 0.685 & 9.3 \\
KNN & 0.771 & 0.751 & 0.755 & 0.749 & 12.8 \\
SVM (RBF) & \textbf{0.835} & \textbf{0.816} & \textbf{0.813} & \textbf{0.821} & 6588.2 \\
Random Forest & 0.791 & 0.772 & 0.772 & 0.772 & 129.7 \\
XGBoost & 0.812 & 0.789 & 0.797 & 0.786 & 36.9 \\
\bottomrule
\end{tabular}
\caption{Validation set performance metrics and training time for all models.}
\label{tab:results}
\end{table}

SVM with RBF kernel got the best results: 83.5\% accuracy and 81.6\% F1-Macro. Precision and recall are balanced (81.3\% and 82.1\%), showing no bias toward false positives or negatives. But training took 6588 seconds (about 110 minutes), which was a problem during experiments.

\subsection{Model-Specific Analysis}

\textbf{Logistic Regression.} We started with Logistic Regression as a baseline. It got 68.1\% F1-Macro, which confirmed that the relationship between features and Nutri-Score is non-linear (see EDA). The model had difficulty with middle classes (B and C), often confusing them with the ones close to them. This makes sense because the Nutri-Score uses step functions and thresholds, not smooth transitions. We tried polynomial features to add non-linearity, but it only improved F1-Macro to 0.69 while making the feature space much larger.

\textbf{K-Nearest Neighbors.} For KNN, validation F1-Macro was good at 75.1\%, but training accuracy got to 99.3\% versus only 77.1\% on validation -- a 22 gap. We tested k values from 3 to 50 and selected k=15, but overfitting remained a problem. The problem seems to be how nutritional data works. Products can look very similar on most features but differ a lot on one nutrient. Since KNN treats all features equally in distance, it just memorizes training examples instead of learning what actually is needed.

\textbf{Support Vector Machine.} SVM with RBF kernel had the best performance at 81.6\% F1-Macro. It was very good at handling class B (the smallest class), where the others failed. The RBF kernel works well because it can model complex decision boundaries. The Nutri-Score formula has different thresholds for different nutrients plus interaction effects (like fruits/vegetables / sugar), and RBF captures these. However, 6588 seconds (1.83 hours) training time was too long. We had to limit hyperparameter search because of this. We tried LinearSVC as a faster option, but it got only 0.66 F1-Macro, worse than Logistic Regression. For a real system that needs online updating on new Open Food Facts data, this training time isn't practical.

\textbf{Random Forest.} Random Forest got 77.2\% F1-Macro in about 2 minutes. Random Forest handled class imbalance well. The main issue was that it preferred middle classes (C and D) over extremes (A and E). This happens because when trees disagree, averaging pulls predictions toward the center.

\textbf{XGBoost.} For practical use, XGBoost was the best. It got 78.9\% F1-Macro in 37 seconds -- the best performance-to-speed ratio. We tuned hyperparameters and found learning rate was critical. 0.3 caused overfitting, 0.01 underfit even with 500 rounds. Best results came from learning rate 0.1. XGBoost also handled missing values well during prediction.

\subsection{Cross-Validation Results}

The 5-fold cross-validation confirmed our validation findings (Table \ref{tab:cv_results}). Standard deviations were consistently low (all under 0.003), meaning performance stayed stable across different data splits. This gave us confidence our train/validation split wasn't unusual. We expected more variance given the noisy crowdsourced data, but stratified splitting plus large fold size (35,000 samples each) handled it.

\begin{table}[h]
\centering
\begin{tabular}{lcc}
\toprule
\textbf{Model} & \textbf{Mean CV Score} & \textbf{Std Dev} \\
\midrule
Logistic Regression & 0.706 & 0.001 \\
KNN & 0.765 & 0.001 \\
SVM (RBF) & 0.832 & 0.001 \\
Random Forest & 0.791 & 0.002 \\
XGBoost & 0.811 & 0.003 \\
\bottomrule
\end{tabular}
\caption{5-fold cross-validation F1-Macro scores on the training set.}
\label{tab:cv_results}
\end{table}

\subsection{Error Analysis}

Looking at confusion matrices, all models showed similar error patterns. They often confused adjacent grades (C as D, B as C), which makes sense for products near grade boundaries. Big errors (predicting E for an A product) were rare but more common with Logistic Regression and KNN, usually on weird nutritional profiles. Class B was hardest to predict -- it's both the smallest class (11.6\%) and has a narrow nutritional range between A and C.

We tested feature engineering impact by running XGBoost with only raw features (no ratios, engineered features, or PCA). F1-Macro dropped from 78.9\% to 71.2\% -- a 7.7 point decrease. This shows engineered features like \texttt{sugar\_to\_carb\_ratio} and \texttt{energy\_density} really help.

We manually checked 100 misclassified XGBoost predictions: 35\% were borderline cases near thresholds; 28\% had missing \texttt{fruits-vegetables-nuts} data that would probably change the grade; 20\% were unusual products (oils, supplements, spices); 12\% looked like labeling errors in the dataset; only 5\% were true model failures. The low rate of real errors suggests we're close to the best we can do with this data.

\subsection{Key Findings}

\textbf{Non-linearity matters.} The gap between Logistic Regression (68.1\%) and non-linear models is significant. Nutri-Score uses thresholds and interactions that linear models can't handle well.

\textbf{Ensemble methods balance performance and speed.} SVM performed best, but Random Forest and XGBoost came within 4-5 points at much lower cost. The 500x speed difference between XGBoost (37s) and SVM (6588s) matters for real deployment.

\textbf{Feature engineering helps.} Our ablation test showed engineered features added 7.7 points. Nutritional ratios provide context -- 10g sugar means different things if total carbs are 80g vs. 15g.

\textbf{Missing fruit/vegetable data limits performance.} This feature is important for the official formula, especially for distinguishing A from B. We had to drop it (95\%+ missing), which probably causes errors in healthier grades.

Getting ~80\% F1-Macro on this noisy dataset seems reasonable. We're approximating a deterministic formula with ML, which inherently adds error. But this lets us classify products that would otherwise have no grade. For Open Food Facts, even imperfect predictions are useful.











\section{Conclusions}

% To be filled with summary of results, strengths, limitations, and future work

\begin{thebibliography}{9}
\bibitem{ncdalliance}
NCD Alliance. \textit{Unhealthy Diets}. \url{https://ncdalliance.org/explore-ncds/risk-factors/unhealthy-diets}

\bibitem{ensemble}

\bibitem{imputation}
ResearchGate. \textit{Evaluating missing value imputation methods for food composition databases}. \url{https://www.researchgate.net/publication/341157370_Evaluating_missing_value_imputation_methods_for_food_composition_databases}

\bibitem{geron2022hands}
Aurélien Géron. \textit{Hands-On Machine Learning with Scikit-Learn, Keras, and TensorFlow: Concepts, Tools, and Techniques to Build Intelligent Systems}, 3rd Edition. O'Reilly Media, 2022.

\bibitem{arora2025applicationmachinelearningpredict}
Nalin Arora, Aviral Chauhan, Siddhant Rana, Mahansh Aditya, Sumit Bhagat, Aditya Kumar, Akash Kumar, Akanksh Semar, Ayush Vikram Singh, Ganesh Bagler. \textit{Application of machine learning to predict food processing level using Open Food Facts}, 2025. \url{https://arxiv.org/abs/2512.17169}

@misc{pycountry2023,
  author = {{Flying Circus}},
  title = {pycountry: ISO country, subdivision, language, currency and script definitions and translations},
  year = {2023},
  url = {https://github.com/flyingcircusio/pycountry},
  note = {Python package version 22.3.5}
}

\end{thebibliography}

\end{document}


